Forecasting Gamma-Ray Bursts using Gravitational Waves

### 2018-11-21 Paper/Manuscript.tex
New manuscript finished post referee report.

\begin{abstract}
We explore the intriguing possibility of employing future ground-based gravitational-wave interferometers to detect the inspiral of binary neutron stars sufficiently
early to alert electromagnetic observatories so that a gamma-ray burst (GRB) can be observed in its entirety from its very beginning.
We quantify the ability to predict a GRB by computing the time a binary neutron star (BNS) system takes to inspiral from its moment of detection to its final merger. We define the moment of detection to be the instant at which the interferometer network accumulates a signal-to-noise ratio of 15. %for the BNS inspiral.
For our computations, %of advance warning times, 
we specifically consider BNS systems at luminosity distances of (i) $D\le200\,$Mpc for the three-interferometer Advanced-LIGO-Virgo network of 2020, and (ii) $D \le 1000\,$Mpc for Einstein Telescope's B and C configurations. 
In the case of Advanced LIGO-Virgo we find that we may at best get a few minutes of warning time, thus we expect no forecast of GRBs in the 2020s. 
On the other hand, Einstein Telescope will provide us with advance warning times of more than five hours for $D \le 100\,$Mpc.
Taking one hour as a benchmark advance warning time, we obtain a corresponding range of roughly 600 Mpc for the Einstein Telescope C configuration.
%, more specifically, greater than an hour
%for BNS inspirals closer than roughly 600\,Mpc. Taking this luminosity distance to be our horizon distance, 
Using current BNS merger event rates within this volume, we show that Einstein C will forecast $\gtrsim \ord(10^2)$ GRBs in the 2030s. %with Einstein C. %with the C configuration of Einstein Telescope.
We reapply our warning-time computation to binary black hole - neutron star inspirals and find that we expect 1 to 3 tidal disruption events 
to be forecast by the same detector.
This article is intended as a pedagogical introduction to gravitational-wave astronomy written at a level accessible to
Ph.D. students, advanced undergraduates, and colleagues in astronomy and/or astrophysics who wish to learn more about the underlying physics.
Though many of our results may be known to the experts, they might nonetheless find this article motivating and exciting.

\todo{1) See end of Sec. IV on page 13, 2) Finish new Sec VIII on BH-BH inspirals, 3) page 19. footnote}
\end{abstract}
\maketitle

@@

%Let us emphasize that this article is intended as a pedagogical introduction to gravitational-wave astronomy written at a level accessible to
%Ph.D. students, advanced undergraduates, and colleagues in astronomy and/or astrophysics who wish to learn more about the underlying physics.
%Be that as it may, even the experts might find our results motivating and exciting.
%
This article is organized as follows. Sec.~\ref{sec:BNS_inspiral} introduces the formulation for the leading-order evolution of the binary inspiral.
Sec.~\ref{sec:IFO_response} details the interferometer response to GWs based on interferometer topology.
Sec.~\ref{sec:idealizations} lists the various idealizations we employ to simplify our treatment and supplies justification for each.
Sec.~\ref{sec:GW170817} tests our model network and evolution using the parameters of GW170817 and the corresponding observations.
Sec.~\ref{sec:results} contains our main results presented as advance warning times in Tables~\ref{table:LIGO2020} and \ref{table:ET}; 
and as ranges and event rates in Table~\ref{table:horizon}.
In Sec.~\ref{sec:BH_NS}, we recompute the advance warning times in the case of binary black hole - neutron star inspirals to see whether or not 
future detectors can forecast tidal disruption events, for which we summarize our findings in Table~\ref{table:ET_BH_NS}.
We then reapply our framework to binary black hole inspirals in Sec.~\ref{sec:BH_BH}.

@@

In a network of $N$ interferometers, the total SNR is defined as follows \cite{Finn:2000hj}
%%
%
\be
\rho_\text{tot} = \left[{\sum_{i=1}^N \rho^2_i}\right]^{1/2}\, , \label{eq:SNR_total}
\ee
%
%%
where Eq.~(\ref{eq:SNR_v2}) is employed to compute $\rho^2_i$ of individual interferometers each with a specific quality factor $Q_i$.
Here, instead of working with specific quality factors of the LIGO and the Virgo interferometers, we consider
a \emph{model network} of three IFOs ($N=3$), where one operates at the RMS average; thus it has $|Q|=2/5$. 
The second IFO is near-optimally oriented/positioned so we assign it a quality
factor one $\sigma$ above the average: $|Q|=2/5+\sigma=4/5$.
It remains to assign a quality factor to the third IFO. We wish to make this operate below the RMS average, % in terms of its orientation and the sky location of the sources,
but it would be pointless to simply set $Q=0$. We therefore pick the values $\iota=0$ (i.e, $|h_+|=|h_\times|$)
and $\psi=0$ for simplicity %(aligning the $x$-axis of the ``$+$'' with the of the IFO
then introduce the following $\{\theta,\phi\}$-only averages
%
\be
 \langle F_+^2\rangle_{\theta,\phi} = \frac{7}{30},\qquad \langle F_\times^2\rangle_{\theta,\phi} = \frac{1}{6}\, 
\ee
yielding
%
\be
\langle |Q(\theta,\phi,\psi=0,\iota=0)|^2 \rangle_{\theta,\phi} = \f{2}{5} \label{eq:RMS_th_phi}.
\ee
Using this value, we assign our below-average third IFO %$\langle|Q|^2\rangle^{1/2}
$|Q|=4/5-\sqrt{2/5}\simeq 0.1675$.
%which is essentially a $\{\theta$-$\phi\}$-RMS awayfrom the overall RMS averaged value of 2/5.
This may seem somewhat ad hoc, 
but it is our way of representing the sub-RMS-average response of the third IFO due to its sub-optimal configuration. 
One may very well use another scheme to generate this below-average response.
Given that $\rho_\text{tot}$ is a sum of quadratures the lowest SNR contributes a small percentage to this [cf. Eq.~(\ref{eq:SNR_total})].

@@

\item {\it Changing the detection threshold from $\bar{\rho}_\text{tot}=15$.}\\
\todo{ADD SNR=12 and 20 computations for ET-C}
$\bar\rho$ is defined in Sec. V
%Furthermore, the physical quantities that we actually observe are blind to this redshift correction. Only after high-precision measurements of
%the chirp mass and the GW polarizations $h_+, h_\times$ can we extract $z$. 
% can be obtained to a very
%high precision in the case of BNSs from the data for $\dot{f}$; e.g., $\mathcal{M}_c = 1.188^{+0.004}_{-0.002}$ for GW170817.
%The ratio $h_+/ h_\times$ gives us the orbital inclination $\iota$.
\end{enumerate}
\section{GW170817 as a test of our model for the Advanced LIGO-Virgo network}\label{sec:GW170817}
On 17 August 2017, at 12:41:04 UTC, GWs from the inspiral and merger of a binary neutron star system %were detected by the Advanced LIGO-Virgo network.
%The event, first picked up by LIGO Hanford (H1), 
swept the ALV network's frequency band from $\approx 30\,$Hz to $\approx 2000\,$Hz, accumulating a total SNR of
%18.8, 26.4 and 2.0 at H1, LIGO Livingstone (L1) and Virgo (V1), respectively, yielding 
$\rho_\text{tot} = 32.4$ \cite{GW170817}.
The inferred duration of the event in the network bandwidth was $\approx 57\,$ seconds during which $\approx 3000$ cycles of GWs were emitted \cite{GW170817_Facts}.
Assuming low-spin priors  ($\chi \le 0.05$, see point 7 of Sec.~\ref{sec:idealizations}), the following updated values were inferred for the total mass, the chirp mass,
and the luminosity distance of the source with 90\% confidence \cite{GW170817_2018}:
M = 2.73^{+0.04}_{-0.01} M_\odot,\quad M_c = 1.186^{+0.001}_{-0.001} M_\odot,\quad D= 40.7^{+2.36}_{-2.36}\,\text{Mpc}. \label{eq:GW170817_params}
Note that the error bar for the chirp mass is very small
due to the fact that it can be extracted to high precision over thousands of GW cycles via Eq.~(\ref{eq:fdot}). 
%In fact, detailed follow-up analyses () have recently restricted the above-values to
%$ \left\{2.73^{+0.04}_{-0.01} M_\odot, 1.186^{+0.001}_{-0.001}M_\odot , 40.7^{+2.36}_{-2.36}\text{Mpc}\right\}$, respectively,
%where the errors in $D$ are at $1\sigma$ level.

@@

$M_c, M$ \cite{Farr:2015lna}; (ii) source sky localization to $\lesssim 5\,\text{Deg}^2$ \cite{Rodriguez:2013oaa};

@@

Erring on the side of optimism, we conclude that the 2030s hold in store real-time observations of dozens to hundreds of gamma-ray bursts and the subsequent kilonovae

@@

which is roughly in line with the timeline of the milli-Hertz space interferometer LISA \cite{Audley:2017drz} and may be five to ten years ahead of CE \todo{citation}}.

@@

100 &   28.2\,minutes & 503 &{\qquad} &  2.15\,hours & 601\T\\
200 & 8.21\,minutes & 251  &{\qquad} & 1.10\,hours & 300 \\
400 &  2.00\,minutes & 124 &{\qquad} & 34.2\,minutes & 148\\
1000 & 14.3\,seconds & 49 &{\qquad} & 13.9\,minutes& 58.5\\
\hline\hline
%bottomrule
\end{tabular}
\caption{Same as Table~\ref{table:ET}, but now for a $5 M_\odot- 1.4 M_\odot$ black hole-neutron star binary.
The SNRs are even higher than before, however the advance warning times have decreased significantly.}\label{table:ET_BH_NS}
\end{table}
%
%

From the table, we can see that the range of ET-C for these binaries with $T_\text{AW} \approx 1\,$hour is roughly 200\,Mpc.
Given that the LIGO O1 merger rate for these systems is $ R < 3600\,$Gpc$^{-3}$yr$^{-1}$ \cite{Abbott:2016ymx},
there could be $\approx 30$ such mergers per year within ET-C's range of $\approx 200\,$Mpc. %corresponding roughly to $T_\text{AW}\approx1\,$hour.
We must emphasize that this should be viewed
as an upper limit as low-mass, high-spin black holes such as ours above are expected to be rare.
Theoretical studies indicate that $\lesssim 10\%$ stellar-mass BHs have masses $\lesssim 5 M_\odot$ \cite{Fryer:1999ht}.
This seems to be supported at least by observations of galactic black holes \cite{Ozel:2010su}.
Therefore, we realistically expect ET-C to forecast $\lesssim 3$ tidal disruption events per year.
%A better estimation would need to incorporate the percentage of such black holes from population studies and Monte-Carlo simulations,
%however, all of these come with rather large error bars.
%and that no TD occurs for $a=0$. This is roughly consistent with Fig.5 of Ref.~\cite{Hanna:2008um}
%Choosing lower mass implies reduced SNR since $\rho \propto M_c^{5/3} \propto (1+Q)^{1/3}/Q$,
%but even with $m_2=5 M_\odot$, a BH-NS binary is ``louder'' than a BNS system at the same distance. 
%and as we showed in Sec.~\ref{sec:results}, low SNR is not going to be a problem with ET sensitivities out to $D \sim 1\,$Gpc.
%
%It is straightforward to show that this mass bound is only consistent with spinning black holes by substituting the naive Schwarzschild $r_\text{ISCO}$ value 
%into Eq~.(\ref{eq:TD_cond1}) along with $c_R=1.7$ {\bf CITE} which yield $M_\text{BH} \lesssim 4.1 M_\odot$ violating the above BH mass bound.
%ISCO location from NR 
%\be
%\Omega_\text{ISCO} M = 0.068 \left[ 1- \f{0.444}{Q^{1/4}}(1-3.54 C^{1/3})\right] 
%\ee
%
\section{Bnary black hole inspirals}\label{sec:BH_BH}
We briefly repeat our computations for binary black hole (BBH) inspirals.
As it is clear that heavier systems inspiral too fast, we limit ourselves
to $5M_\odot-5M_\odot$ BBHs and only consider ET-C.
\todo{Finish this}

>>>>

\begin{abstract}
We explore the intriguing possibility of employing future ground-based gravitational-wave interferometers to detect the inspiral of binary neutron stars sufficiently
early to alert electromagnetic observatories so that a gamma-ray burst (GRB) can be observed in its entirety from its very beginning.
We quantify the ability to predict a GRB by computing the time a binary neutron star (BNS) system takes to inspiral from its moment of detection to its final merger. We define the moment of detection to be the instant at which the interferometer network accumulates a signal-to-noise ratio of 15. %for the BNS inspiral.
For our computations, %of advance warning times, 
we specifically consider BNS systems at luminosity distances of (i) $D\le200\,$Mpc for the three-interferometer Advanced-LIGO-Virgo network of 2020, and (ii) $D \le 1000\,$Mpc for Einstein Telescope's B and C configurations. 
In the case of Advanced LIGO-Virgo we find that we may at best get a few minutes of warning time, thus we expect no forecast of GRBs in the 2020s. 
On the other hand, Einstein Telescope will provide us with advance warning times of more than five hours for $D \le 100\,$Mpc.
Taking one hour as a benchmark advance warning time, we obtain a corresponding range of roughly 600 Mpc for the Einstein Telescope C configuration.
%, more specifically, greater than an hour
%for BNS inspirals closer than roughly 600\,Mpc. Taking this luminosity distance to be our horizon distance, 
Using current BNS merger event rates within this volume, we show that Einstein C will forecast $\gtrsim \ord(10^2)$ GRBs in the 2030s. %with Einstein C. %with the C configuration of Einstein Telescope.
We reapply our warning-time computation to binary black hole - neutron star inspirals and find that we expect 1 to 3 tidal disruption events 
to be forecast by the same detector.
This article is intended as a pedagogical introduction to gravitational-wave astronomy written at a level accessible to
Ph.D. students, advanced undergraduates, and colleagues in astronomy and/or astrophysics who wish to learn more about the underlying physics.
Though many of our results may be known to the experts, they might nonetheless find this article motivating and exciting.
\end{abstract}
\maketitle

@@

%Let us emphasize that this article is intended as a pedagogical introduction to gravitational-wave astronomy written at a level accessible to
%Ph.D. students, advanced undergraduates, and colleagues in astronomy and/or astrophysics who wish to learn more about the underlying physics.
%Be that as it may, even the experts might find our results motivating and exciting.
%
This article is organized as follows. Sec.~\ref{sec:BNS_inspiral} introduces the formulation for the leading-order evolution of the binary inspiral.
Sec.~\ref{sec:IFO_response} details the interferometer response to GWs based on interferometer topology.
Sec.~\ref{sec:idealizations} lists the various idealizations we employ to simplify our treatment and supplies justification for each.
Sec.~\ref{sec:GW170817} tests our model network and evolution using the parameters of GW170817 and the corresponding observations.
Sec.~\ref{sec:results} contains our main results presented as advance warning times in Tables~\ref{table:LIGO2020} and \ref{table:ET}; 
and as ranges and event rates in Table~\ref{table:horizon}.
In Sec.~\ref{sec:BH_NS}, we recompute the advance warning times in the case of binary black hole - neutron star inspirals to see whether or not 
future detectors can forecast tidal disruption events, for which we summarize our findings in Table~\ref{table:ET_BH_NS}.
%We then reapply our framework to binary black hole inspirals in Sec.~\ref{sec:BH_BH}.

@@

In a network of $N$ interferometers, the total SNR is defined as follows \cite{Finn:2000hj}
%%
%
\be
\rho_\text{tot} = \left[{\sum_{i=1}^N \rho^2_i}\right]^{1/2}\, , \label{eq:SNR_total}
\ee
%
%%
where Eq.~(\ref{eq:SNR_v2}) is employed to compute $\rho^2_i$ of individual interferometers each with a specific quality factor $Q_i$.
Here, instead of working with specific quality factors of the LIGO and the Virgo interferometers, we consider
a \emph{model network} of three IFOs ($N=3$), where one operates at the RMS average; thus it has $|Q|=2/5$. 
The second IFO is better oriented/positioned so we assign it a quality
factor one $\sigma$ above the average: $|Q|=2/5+\sigma=4/5$.
It remains to assign a quality factor to the third IFO. We wish to make this operate below the RMS average, % in terms of its orientation and the sky location of the sources,
but it would be pointless to simply set $Q=0$. We therefore pick the values $\iota=0$ (i.e, $|h_+|=|h_\times|$)
and $\psi=0$ for simplicity %(aligning the $x$-axis of the ``$+$'' with the of the IFO
then introduce the following $\{\theta,\phi\}$-only averages
%
\be
 \langle F_+^2\rangle_{\theta,\phi} = \frac{7}{30},\qquad \langle F_\times^2\rangle_{\theta,\phi} = \frac{1}{6}\, 
\ee
yielding
%
\be
\langle |Q(\theta,\phi,\psi=0,\iota=0)|^2 \rangle_{\theta,\phi} = \f{2}{5} \label{eq:RMS_th_phi}.
\ee
Using this value, we assign our below-average third IFO %$\langle|Q|^2\rangle^{1/2}
$|Q|=4/5-\sqrt{2/5}\simeq 0.1675$.
%which is essentially a $\{\theta$-$\phi\}$-RMS awayfrom the overall RMS averaged value of 2/5.
This may seem somewhat ad hoc, 
but it is our way of representing the sub-RMS-average response of the third IFO due to its sub-optimal configuration. 
One may very well use another scheme to generate this below-average response.
Given that $\rho_\text{tot}$ is a sum of quadratures the lowest SNR contributes a small percentage to this [cf. Eq.~(\ref{eq:SNR_total})].

@@

\item {\it Changing the detection criterion from} $\bar{\rho}_\text{tot}=15$. 
In sections \ref{sec:results} - \ref{sec:BH_NS}, we present our results for advance warning times based on a detection criterion
given by total network SNR equalling 15 [cf. Eq.~(\ref{eq:SNR_bar})].
It is quite common in the literature to select 8 or 12 for $ \bar\rho_\text{tot} $.
So, here, we briefly explore the consequences of (i) relaxing our detection criterion to $\bar{\rho}_\text{tot}=12$, and (ii) making it more strict by setting $\bar{\rho}_\text{tot}=20$.
The former choice provides longer warning times and the latter less.
We recommend first the reading of Secs.~\ref{sec:GW170817}, \ref{sec:results} before continuing here.

For the ALV network of 2020s, it is clear from the results in Table~\ref{table:LIGO2020} that
there is no point in discussing the $\bar{\rho}_\text{tot}=20$ case as that would result in advance
warning times of mere seconds. So we only consider $\bar{\rho}_\text{tot}=12$ and BNS inspirals at $D=50,100\,$Mpc for which we find that the advance warning times increase to 120 and 36 seconds from 86 and 23, respectively. Though this is an improvement, it does not change our conclusion to Sec.~\ref{Sec:ALIGO2020}, that we expect no forecasts in the 2020s.

For Einstein Telescope, we consider both $\bar{\rho}_\text{tot}=12$ and 20 given its low-frequency sensitivity. We present the resulting advance warning times ($T_\text{AW}$) in Table~\ref{table:SNR_12_20_results}
on the next page. Comparing these with the corresponding ones in Table~\ref{table:ET}, we see that setting
$\bar{\rho}_\text{tot}=12$ increases ET-B, C warning times by $\gtrsim 50\%, \sim 20\%$, respectively.
On the other hand, $\bar{\rho}_\text{tot}=20$ decreases them by $\sim 40\%, 20\%$.
Be that as it may, we see that ET-C sensitivity still yields advance warning times $> 1\,$hour for sources within $\approx 450$\,Mpc. Therefore, our conclusions that we expect ET-C to forecast $\gtrsim 5$ yearly
BNS mergers holds.

\begin{table}[h]
\centering
\begin{tabular}{lccccc}
%toprule
\hline\hline
$D\,$(Mpc)\hspace{2mm} & \multicolumn{2}{c}{$T_\text{AW}(\bar{\rho}_\text{tot}=12)$} & & \multicolumn{2}{c}{$T_\text{AW}(\bar{\rho}_\text{tot}=20)$}\T\B\\
\hline
{}& ET-B & ET-C &\hspace{5mm} & ET-B & ET-C  \T\B\\
%midrule
100 & 70\,minutes & 6.6\,hours & & 28\,minutes & 4.2\,hours \\
200 & 18\,minutes & 3.4\,hours & & 7.0\,minutes & 2.2\,hours \\
400 & 4.6\,minutes & 1.8\,hours & & 1.5\,minutes & 1.2\,hours \\
1000 & 31\,seconds & 44\,minutes & & 6.2\,seconds & 24\,minutes \\
\hline\hline
\end{tabular}
\caption{Alternative advance warning times obtained using detection criteria of $\bar{\rho}_\text{tot}=12,20$ as opposed to 15 which is our standard choice throughout this article for which the ET-B/C results are displayed in Table~\ref{table:ET}.}\label{table:SNR_12_20_results}
\end{table}
%
%
%
%
%Furthermore, the physical quantities that we actually observe are blind to this redshift correction. Only after high-precision measurements of
%the chirp mass and the GW polarizations $h_+, h_\times$ can we extract $z$. 
% can be obtained to a very
%high precision in the case of BNSs from the data for $\dot{f}$; e.g., $\mathcal{M}_c = 1.188^{+0.004}_{-0.002}$ for GW170817.
%The ratio $h_+/ h_\times$ gives us the orbital inclination $\iota$.
\end{enumerate}
%
%
%
\section{GW170817 as a test of our model for the Advanced LIGO-Virgo network}\label{sec:GW170817}
On 17 August 2017, at 12:41:04 UTC, GWs from the inspiral and merger of a binary neutron star system %were detected by the Advanced LIGO-Virgo network.
%The event, first picked up by LIGO Hanford (H1), 
swept the ALV network's frequency band from $\approx 30\,$Hz to $\approx 2000\,$Hz, accumulating a total SNR of
%18.8, 26.4 and 2.0 at H1, LIGO Livingstone (L1) and Virgo (V1), respectively, yielding 
$\rho_\text{tot} = 32.4$ \cite{GW170817}.
The inferred duration of the event in the network bandwidth was $\approx 57\,$ seconds during which $\approx 3000$ cycles of GWs were emitted \cite{GW170817_Facts}.
Assuming low-spin priors  ($\chi \le 0.05$, see point 7 of Sec.~\ref{sec:idealizations}), the following updated values were inferred for the total mass, the chirp mass,
and the luminosity distance of the source with 90\% confidence \cite{GW170817_2018}:
%
\be
M = 2.73^{+0.04}_{-0.01} M_\odot,\quad M_c = 1.186^{+0.001}_{-0.001} M_\odot,\quad D= 40.7^{+2.36}_{-2.36}\,\text{Mpc}. \label{eq:GW170817_params}
\ee
%
Note that the error bar for the chirp mass is very small
due to the fact that it can be extracted to high precision over thousands of GW cycles via Eq.~(\ref{eq:fdot}). 
%In fact, detailed follow-up analyses () have recently restricted the above-values to
%
%$ \left\{2.73^{+0.04}_{-0.01} M_\odot, 1.186^{+0.001}_{-0.001}M_\odot , 40.7^{+2.36}_{-2.36}\text{Mpc}\right\}$, respectively,
%
%where the errors in $D$ are at $1\sigma$ level.

@@

$M_c, M$ \cite{Farr:2015lna}; (ii) source sky localization to $\lesssim 5\,\text{deg}^2$ \cite{Rodriguez:2013oaa};

@@

Therefore, erring on the side of optimism, we conclude that the 2030s hold in store real-time 
electromagnetic observations of at least dozens of gamma-ray bursts and the subsequent kilonovae

@@

which is roughly in line with the timeline of the milli-Hertz space interferometer LISA \cite{Audley:2017drz} and CE \cite{LIGO_inst}.}.

@@

100 &   28.2\,minutes & 503 &{\qquad} &  2.17\,hours & 601\T\\
200 & 8.21\,minutes & 251  &{\qquad} & 1.10\,hours & 300 \\
400 &  2.00\,minutes & 124 &{\qquad} & 34.2\,minutes & 148\\
1000 & 14.3\,seconds & 49.0 &{\qquad} & 13.9\,minutes& 58.5\\
\hline\hline
%bottomrule
\end{tabular}
\caption{Same as Table~\ref{table:ET}, but now for a $5 M_\odot- 1.4 M_\odot$ black hole-neutron star binary.
The SNRs are even higher than before, however the advance warning times have decreased significantly.}\label{table:ET_BH_NS}
\end{table}
%
%

From the table, we can see that the range of ET-C for these binaries with $T_\text{AW} \approx 1\,$hour is roughly 200\,Mpc.
Given that the LIGO O1 merger rate for these systems is $ R < 3600\,$Gpc$^{-3}$yr$^{-1}$ \cite{Abbott:2016ymx},
there could be $\approx 30$ such mergers per year within ET-C's range of $\approx 200\,$Mpc. %corresponding roughly to $T_\text{AW}\approx1\,$hour.
We must emphasize that this should be viewed
as an upper limit as low-mass, high-spin black holes such as ours above are expected to be rare.
Theoretical studies indicate that $\lesssim 10\%$ stellar-mass BHs have masses $\lesssim 5 M_\odot$ \cite{Fryer:1999ht}.
This seems to be supported at least by observations of galactic black holes \cite{Ozel:2010su}.
Therefore, we realistically expect ET-C to forecast $\lesssim 3$ tidal disruption events per year.
%A better estimation would need to incorporate the percentage of such black holes from population studies and Monte-Carlo simulations,
%however, all of these come with rather large error bars.
%and that no TD occurs for $a=0$. This is roughly consistent with Fig.5 of Ref.~\cite{Hanna:2008um}
%Choosing lower mass implies reduced SNR since $\rho \propto M_c^{5/3} \propto (1+Q)^{1/3}/Q$,
%but even with $m_2=5 M_\odot$, a BH-NS binary is ``louder'' than a BNS system at the same distance. 
%and as we showed in Sec.~\ref{sec:results}, low SNR is not going to be a problem with ET sensitivities out to $D \sim 1\,$Gpc.
%
%It is straightforward to show that this mass bound is only consistent with spinning black holes by substituting the naive Schwarzschild $r_\text{ISCO}$ value 
%into Eq~.(\ref{eq:TD_cond1}) along with $c_R=1.7$ {\bf CITE} which yield $M_\text{BH} \lesssim 4.1 M_\odot$ violating the above BH mass bound.
%ISCO location from NR 
%\be
%\Omega_\text{ISCO} M = 0.068 \left[ 1- \f{0.444}{Q^{1/4}}(1-3.54 C^{1/3})\right] 
%\ee
%

%\section{Binary black hole inspirals}\label{sec:BH_BH}
For the curious reader, we briefly repeat our computations for binary black hole (BBH) inspirals.
As heavier systems inspiral too fast, we limit ourselves
to $5M_\odot-5M_\odot$ BBHs and only consider only ET-C.
For these systems, we find that $T_\text{AW} \lesssim 1\,$hour for $D\gtrsim 190\,$Mpc, but $\bar{\rho}_F$ exceeds 500 due to the increased total mass. Even for a source at 100\,Mpc, we obtain $T_\text{AW}\approx 35\,$minutes at best.
As such lightweight black holes
are expected to be rare and given the current BBH merger rate of 12-213\,Gpc$^{-3}$yr$^{-1}$ \cite{Abbott:2017vtc}, which translates to $\ord(0.1) - \ord(1)$ BBH mergers yearly
within 190\,Mpc, we statistically expect no forecasts of these events. 
Nonetheless, ET and CE will detect hundreds to thousands of BBH mergers out to redshifts of $z> 10$.
